Really Good Title

### 2019-01-07 documentation/paper.tex
All vs best

\section{Per-individual self adaptation}

@@

We first implemented a method similar to (4) from \cite{self_adapt}, giving each individual a mutation rate and a sigma value. These were mutated when the individual was selected for mutation. Their initialization was also random, in the range of [0.25, 0.75] for the mutation rate and [0, 0.03] for the sigma values.

@@

We also explored a method similar to (5) in \cite{self_adapt}, where each parameter gets it's own mutation sigma parameter. This produces similar results to per-individual self adaptation with harsh teachers, but with benevolent teachers fails to reproduce the consistency of the other method.

@@

It's possible that with increasing the number of generations this algorithm would produce some advantages over training with just one teacher. Sadly, this would have to repeat all the previous experiments with a higher generation count for comparability's sake.

@@

\section{Self-training}

\subsection{last best}

\begin{figure}[H]
\center
\includegraphics[width=0.155555\textwidth]{img/scheme_self_training_1.png}
\caption{Scheme for self training variant 1}
\label{fig:scheme_self_training_1}
\end{figure}

Fitness evaluated with the best bot of the last generation.

@@

\todo{risk to end up in local optimum like self adapt 1?}

\subsection{two species}

\begin{figure}[H]
\center
\includegraphics[width=0.155555\textwidth]{img/scheme_self_training_1.png}
\caption{Scheme for self training variant 1}
\label{fig:scheme_self_training_2}
\end{figure}

>>>>

\section{Per-individual self adaptation}
\label{sec:perind}

@@

We first implemented a method similar to (1) and (4) from \cite{self_adapt}, giving each individual a mutation rate and a sigma value. These were mutated when the individual was selected for mutation. Their initialization was also random, in the range of [0.25, 0.75] for the mutation rate and [0, 0.03] for the sigma values.

@@

We also explored a method similar to (2) and (5) in \cite{self_adapt}, where each parameter gets it's own mutation sigma parameter. This produces similar results to per-individual self adaptation with harsh teachers, but with benevolent teachers fails to reproduce the consistency of the other method.

@@

It's possible that with increasing the number of generations this algorithm would produce some advantages over training with just one teacher, but we couldn't finish the longer experiment due to time constraints.

@@

\section{Self-training}
Implementing self-training based on \cite{Sims94evolving3d}.

\subsection{All vs best}
We ran a version of the algorithm where the fitness function was evaluated on the best specimen of the last generation.

\begin{figure}[H]
\center
\includegraphics[width=0.155555\textwidth]{img/scheme_self_training_1.png}
\caption{Scheme for all vs best training; source: \cite{Sims94evolving3d}.}
\label{fig:scheme_self_training_1}
\end{figure}

@@

Since we start out with evaluating against easy opponents, it's a possibility for the algorithm to get stuck in a local optimum like it did with per-individual self adaptation. While the standard method works nice, (see figures \ref{fig:last_best} and \ref{fig:self_training_1}) the self-adaption variant fails to produce any meaningful result despite the high fitness value, thus supporting our theory from section \ref{sec:perind}.

\subsection{Two-species all vs best}

This implementation of the idea from \cite{Sims94evolving3d} uses two species that are always evaluated against the other.

\todo{Did we have two 100 sized pops here?}

\begin{figure}[H]
\center
\includegraphics[width=0.155555\textwidth]{img/scheme_self_training_2.png}
\caption{Scheme for self training variant 1}
\label{fig:scheme_self_training_2}
\end{figure}
